The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-11-29 manuscript/manuscript.qmd
Shift lit review points order and add explanation of the results of timing

3. Exploring differentiated application of these laws - *de facto* vs. *de jure* and differentiated treatment for more vs. less contentious INGOs. Authoritarian -> arbitrary and varied application of the law -> different *operating space*

@@

International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches. Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009]. Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018].

@@

TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space… General crackdown stuff + China crackdown stuff + our addition

@@

## Regulations as policy tool to shape behavior

@@

@@

In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences. @HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift[ed] towards fields of activity high up the government’s domestic policy agenda" [-@HolbigLang:2022, p. 587].

@@

Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge. As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces. Our main variable of interest is thus a mix of continuous outcomes (i.e. a range of provinces) bounded between two discrete outcomes (i.e. one province and all provinces). Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e. negative counts of provinces or more than 32 provinces). If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0–1 range. However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32). To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages. We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.

@@

:::{.column-page-inset}
$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
% Put the huge equation in a nested \begin{aligned}[t] environment so that 
% \mathrlap{} can go around it so that the annotations in the priors can be 
% aligned closer to the math
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$ {#eq-ordbeta}
:::

@@

We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations. As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering. Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily. As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time. As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19--23 provinces, while their locally-focused counterparts are only expected to register in an average of 7--16 provinces. Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later. Further research on this point is warranted.

>>>>

3.  Exploring differentiated application of these laws - *de facto* vs. *de jure* and differentiated treatment for more vs. less contentious INGOs. Authoritarian -\> arbitrary and varied application of the law -\> different *operating space*

@@

International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches. Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009]. Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018; Spires:2020a].

@@

TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space... General crackdown stuff + China crackdown stuff + our addition

@@

@@

## China's Overseas NGO law as a policy tool and its implications

@@

In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences. @HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p. 587].

@@

Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge. As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2--31 provinces. Our main variable of interest is thus a mix of continuous outcomes (i.e. a range of provinces) bounded between two discrete outcomes (i.e. one province and all provinces). Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e. negative counts of provinces or more than 32 provinces). If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0--1 range. However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32). To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages. We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.

@@

::: column-page-inset
$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
% Put the huge equation in a nested \begin{aligned}[t] environment so that 
% \mathrlap{} can go around it so that the annotations in the priors can be 
% aligned closer to the math
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$ {#eq-ordbeta}
:::

@@

We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations. As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering. [@Jia:2017a] Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily. As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time. As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19--23 provinces, while their locally-focused counterparts are only expected to register in an average of 7--16 provinces. Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later. Another possible explanation is interpreting earlier timing in registration as more eager to register as discussed in the measurement section. INGOs that self-perceive as more contentious would be more nervous about the legal consequences of not being able to register and thus be more eager to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018]. Compared with their more "rest-assured" peers, INGOs seeking to register earlier are more likely to have reduced operational space. To understand the underlying mechanism with registration timing, further research is warranted.
